---
title: "quiz 2"
author: "andrew"
date: "11/8/2021"
output: pdf_document
---

# 1. 
Suppose I define the following function in R\
```{r tidy=TRUE}
cube <- function(x, n) {
        x^3
}
```

\ 
What is the result of running cube(3) the following in R after defining this function?\

```{r comment= "Answer:"}
cube(3)
```

# 2. 
The following code will produce a warning in R, why?
\
```{r}
x <- 1:10
if(x > 5) {
        x <- 0
}
```
\
Answer: X is vector and "if" can only test a single logical statement.\

# 3.
Consider the following function.\

```{r}
f <- function(x) {
        g <- function(y) {
                y + z
        }
        z <- 4
        x + g(x)
}
```
\
If i then run in R the following, what value is returned.\

```{r comment= "Answer:"}
z <- 10
f(3)
```
\
# 4.
Consider the following expression, What is the value of 'y' after evaluating this expression?\

```{r comment="Answer:"}
x <- 5
y <- if(x < 3) {
        NA
} else {
        10
}

y
```

\
# 5.
Which symbol in the function is a free variable?\

```{r}
h <- function(x, y = NULL, d = 3L) {
        z <- cbind(x, d)
        if(!is.null(y))
                z <- z + y
        else
                z <- z + f
        g <- x + y / z
        if(d == 3L)
                return(g)
        g <- g + 10
        g
}
```
\ 
Answer: f\

# 6. 
What is an environment in R?\
Answer: a collection of symbol/value pairs\

# 7.
The R language used what type of scoping rule for resolving free variables?\
Answer: Lexical Scoping\

# 8.
How are free variables in R functions resolved?\
Answer: The values of free variables are searched for in the environment in which the function was defined.

# 9.
What is one of the consequences of the scoping rules used in R?\
Answer: All objects must be stored in memory

# 10.
In R, what is the parent frame?
Answer: It is the environment in which a function was called